Using reference models in variable selection \vspace{.1in}

### 2022-02-13 reviews/rebuttal.tex

\begin{point}
Perhaps a solution to the previous problem would be to determine the reference model using frequentist MLE procedures that avoid the construction of prior distributions and use a single point prediction or, alternatively, to use the sampling distribution of MLE as a posterior distribution and take this “Bayesian” model as reference model. Do you have any experience in this line?
\end{point}

\begin{reply}
This is an interesting question. The way we see it is that MLE tends to be more unstable than comparable Bayesian approaches, as the latter get improved stability both from integration over the parameter space (instead of using only a point estimate) and can further be improved by using even just weakly informative priors (rather than improper flat priors). We have added references that discuss the merits of Bayesian approaches compared to MLE. Although we think Bayesian reference models are a better choice in most cases, we also assume that in large $n$, small $p$ cases there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model too.

Inspired by your question, we added a discussion of this in the new version of the paper. In Section 2.2 we write

\vspace{0.5\baselineskip}
\textit{In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
	However, Bayesian methods can help in some of those situations
	where MLE procedures struggle. 
	It is known that, as the number of parameters in the model increases, the MLE
	estimator is dominated by shrinkage estimators 
	\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
	The use of a prior in Bayesian inference automatically incorporates 
	some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
	For the sake of our study, we rely on simple data structure which can be well be described 
	by linear regression models. However, more complex data can arise in practice, for example, including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}

@@

\begin{point}
In most of real situations, we have an M-open problem (particularly in big data problems) where the true generator mechanism is too complex and it is not included in the family of considered models. What would be the performance of your methodology if the reference model is far from the true generator process? How can you detect these situations?
\end{point}

\begin{reply}
We assume that all models are wrong. Analysing model misspecification is well studied in the Bayesian literature and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}. The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}. Even a misspecified model that would introduce some bias can reduce the variance so that the variable selection is improved via an improved bias-variance tradeoff. As the selection is to find a submodel that is not far from the reference model, the performance of the selected model is not far from the reference model.

We have clarified this in the introduction:
\end{reply}

\vspace{0.5\baselineskip}
\textit{
We assume all models are wrong, but we assume we have constructed a
model which reflects our beliefs about the future data in the best
possible way and which has passed model checking and criticism
\citep{gelman2020bayesian,gabry2019visualization}.  Using the usual
best practices for constructing the reference model is important, as
using a bad reference model can only lead to selecting a similarly
bad smaller model. If the reference model is considered to have
useful predictions, then the smaller models selected will also have
similar useful predictions.
}

### 2022-02-13 paper/ref_approach.tex
fixed incoherences between rebuttal and paper

\fede{The goal of our work is to study the impact of reference model approaches
disentangling the benefit of the usage of a reference model from the specific selection algorithm.
Specifically, we:}
% The main contributions of our work are:
\fede
{\begin{itemize}
\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach. This allows us to build up a comparison independent of the specific variable selection method;
% We show a simple and intuitive way to combine any variable selection method with the reference model approach.
\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.
\end{itemize}
}

@@

\fede{In general, there is not restriction on the type of model the reference models 
should be and a sensible reference model does not need to be Bayesian.
However, Bayesian methods can help in some of those situations
where MLE procedures struggle. 
It is known that as the number of parameters in the model increases, the MLE
estimator is dominated by shrinkage estimators 
\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
The use of a prior in Bayesian inference automatically incorporates 
some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
For the sake of our study, we rely on simple data structure which can be well described 
by linear regression models. However, more complex data can arise from applications, for example including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the posterior distribution.}

@@

\subsection{Reference model's effect and the projection predictive approach}
\fede{The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
  %
The simulation study based on artificial data of Section \ref{minimal-simulated} shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection with the reference model approach (see Figure \ref{fig:bodyfat_step_refvsdata} and Table \ref{tab:step_refvsdata}). However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.}

>>>>

\fede{The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms. In particular, we:
\begin{itemize}
	\item propose a simple and intuitive approach to combine any variable selection method with the reference model approach. This allows us to investigate the benefit of using reference models independent of the specific variable selection method;
	\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
	\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimal subset variable selection.
\end{itemize}}

@@

\fede{In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
However, Bayesian methods can help in some of those situations
where MLE procedures struggle. 
It is known that as the number of parameters in the model increases, the MLE
estimator is dominated by shrinkage estimators 
\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
The use of a prior in Bayesian inference automatically incorporates 
some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
For the sake of our study, we rely on simple data structure which can be well described 
by linear regression models. However, more complex data can arise in practice, for example, including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}

@@

\subsection{Reference model's effect and the projection predictive approach}
\fede{The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4). However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.}
